\Large \bf \projtitle

### 2015-05-05 doc/paper/paper.tex
Fix syntax
server implementation

@@

>>>>

There are two main server-side components to \zbf\. First is the tracker,
which maintains a mapping from resource hashes to the peers that have that
resource. Second is the WebRTC handshake channel, which passes information
between peers to enable them to open WebRTC data channels.

@@

WebRTC handshake information--the offers, ICE candidates, and answers--are
sent through the client-side signaling channel through a websocket to
the server. The client-side signaling channel specifies a peer to which
this WebRTC handshake information should be sent; if the server has an open
websocket connection with that peer, the server passes that message to the peer.
